\section{Architecture}

OPD-Vertex uses a layered architecture with a clear dependency direction. Presentation code calls application services, application services depend on domain contracts, and infrastructure modules implement those contracts for databases, AI services, PDF generation, email, and logging.

\begin{figure}[h]
\centering
\begin{tikzpicture}[
  layer/.style={rectangle,rounded corners=2mm,draw=VertexBlue,fill=white,thick,minimum width=10.5cm,minimum height=0.9cm,align=center},
  adapter/.style={rectangle,rounded corners=2mm,draw=VertexTeal,fill=VertexPanel,thick,minimum width=3.1cm,minimum height=0.75cm,align=center},
  arrow/.style={-{Latex[length=2.2mm]},draw=VertexMuted,thick}
]
\node[layer] (presentation) {Presentation: FastAPI routes, request handlers, Jinja templates};
\node[layer,below=0.55cm of presentation] (application) {Application: use-case orchestration and workflow services};
\node[layer,below=0.55cm of application] (domain) {Domain: entities, DTOs, ports, and business contracts};
\node[adapter,below left=0.9cm and -0.1cm of domain] (sql) {SQL repositories};
\node[adapter,right=0.35cm of sql] (mongo) {Mongo repositories};
\node[adapter,right=0.35cm of mongo] (ai) {Local AI adapters};
\node[adapter,below=0.35cm of mongo] (pdf) {PDF and email adapters};
\draw[arrow] (presentation) -- (application);
\draw[arrow] (application) -- (domain);
\draw[arrow] (sql) -- (domain);
\draw[arrow] (mongo) -- (domain);
\draw[arrow] (ai) -- (domain);
\draw[arrow] (pdf) -- (domain);
\end{tikzpicture}
\caption{Layered architecture and adapter direction.}
\end{figure}

\subsection{Persistence Model}

The project intentionally splits transactional and document-oriented data. Relational tables own stable operational records; MongoDB owns evolving AI artifacts and configuration documents.

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{@{}L{0.25\textwidth}Y@{}}
\toprule
\textbf{Store} & \textbf{Owned data} \\
\midrule
MySQL & Staff, patients, consultations, approved prescriptions, and audit logs. \\
MongoDB & Email templates, LLM prompts, generated documents, consultation documents, transcript artifacts, and review artifacts. \\
Shared linkage & \texttt{consultation\_id} connects relational records to document records. \\
\bottomrule
\end{tabularx}
\caption{SQL and MongoDB ownership boundaries.}
\end{table}

\subsection{AI Adapter Boundary}

Transcription and clinical note generation are separate domain ports. This prevents the speech-to-text path from becoming tightly coupled to the report-generation path and allows each adapter to evolve independently. Faster-Whisper handles transcription, while transcript normalization, report generation, and Suggestive Mode use Ollama with \texttt{qwen3:8b}.

\begin{calloutbox}{AI Safety Boundary}
Generated drafts are not treated as final clinical records. They remain draft documents until a doctor reviews and approves them. Approved prescriptions are then projected into SQL, creating a deliberate boundary between probabilistic generation and durable operational data.
\end{calloutbox}

\subsection{Data Flow}

\begin{enumerate}
  \item Browser microphone captures consultation audio.
  \item Faster-Whisper transcribes audio and stores raw transcript text in MongoDB.
  \item The application normalizes the transcript and generates a structured draft report.
  \item Suggestive Mode reviews the draft against the transcript and source context.
  \item The doctor reviews, edits, approves, or rejects the generated report.
  \item Approved prescription information is projected into SQL.
  \item The approved report can be exported to PDF and sent by email.
\end{enumerate}